Staged Abstract Interpreters

### 2018-11-06 paper/10_intro.tex
section refs

\begin{itemize}
\item Starting from a definitional abstract interpreter for a higher-order functional language,
  whose syntax and semantics are described in section \ref{bg_lang},
  we show how to turn it into a staged abstract interpreter (SAI) by adding stage annotations. 
  The design and implementation of SAI using Scala and Lightweight Modular Staging (LMS) framework is 
  described in section \ref{sai}.
  We later extend the staged abstract interpreter to support imperative language features 
  (section \ref{cases_imp}), such as states, loops and exceptions.
\item We demonstrate that the staged abstract interpreter not only improves the \textit{efficiency}
  but also the \textit{scalability}, which are two major issues in static analysis, if we apply it on open
  programs. \todo{more on this point.}
\item To demonstrate the feasibility and applicability of the proposed approach, we conduct three case studies in section \ref{cases_study}. 
  First we revisit Abstract Compilation \cite{Boucher:1996:ACN:647473.727587}, which is a closure generation 
  technique applied on 0-CFA. We show that it can be understood and easily implemented as an instance of 
  our staged abstract interpreter. 
  Second, we demonstrate sophisticated control-flow analysis techniques, such as adaptive context/flow/path-sensitive 
  analysis and store-widening can be integrated with staged abstract interpreters without losing any precision.
  Finally, we show that in an imperative language, the idea can be applied to an abstract interpreter with
  an abstract domain that performs numerical analysis.
  % (Optional: taint/information flow analysis?)
\item We empirically evaluate the performance improvement by staging an big-step abstract interpreter 
  for control-flow analysis. We compare against with the unstaged version, a small-step version (unstaged), 
  and an optimizing small-step version.
\end{itemize}

>>>>

\begin{itemize}
\item Starting from a definitional abstract interpreter for a higher-order functional language,
  whose syntax and semantics are described in Section~\ref{bg_lang},
  we show how to turn it into a staged abstract interpreter (SAI) by adding stage annotations. 
  The design and implementation of SAI using Scala and Lightweight Modular Staging (LMS) framework is 
  described in Section~\ref{sai}.
  We later extend the staged abstract interpreter to support imperative language features 
  (Section~\ref{cases_imp}), such as states, loops and exceptions.
\item We demonstrate that the staged abstract interpreter not only improves the \textit{efficiency}
  but also the \textit{scalability}, which are two major issues in static analysis, if we apply it on open
  programs. \todo{more on this point.}
\item To demonstrate the feasibility and applicability of the proposed approach, we conduct three case studies in Section~\ref{cases_study}. 
  First we revisit Abstract Compilation \cite{Boucher:1996:ACN:647473.727587}, which is a closure generation 
  technique applied on 0-CFA. We show that it can be understood and easily implemented as an instance of 
  our staged abstract interpreter. 
  Second, we demonstrate sophisticated control-flow analysis techniques, such as adaptive context/flow/path-sensitive 
  analysis and store-widening can be integrated with staged abstract interpreters without losing any precision.
  Finally, we show that in an imperative language, the idea can be applied to an abstract interpreter with
  an abstract domain that performs numerical analysis.
  % (Optional: taint/information flow analysis?)
\item We empirically evaluate the performance improvement by staging an big-step abstract interpreter 
  for control-flow analysis. We compare against with the unstaged version, a small-step version (unstaged), 
  and an optimizing small-step version.
\end{itemize}

### 2018-11-06 paper/20_bg.tex
section refs

As higher-order functions had been widely introduced in mainstream programming languages \todo{cite}, in this paper, 
we target a tiny higher-order functional language \TLang, which is based on direct-style lambda-calculus
with the support of numbers, arithmetics, recursions and conditionals.
In section \ref{cases_imp}, we will see adding more imperative features to the language.
Since we are mostly interested in analyzing the dynamic behavior of the program, the static semantics and
type system will be omitted. We also assume all the input programs are well-typed.
The abstract syntax is described below:

@@

Readers may notice an additional abstract type \texttt{R[+T]} is defined in the trait,
which means \texttt{R} represents a higher-kinded type and will used to specify the binding-time, 
i.e., staged or not. Since the LMS framework we are using allows us to specify binding-time purely
based on types, the unstaged higher-kinded type can be simply instantiated as an identity type constructor: 
\texttt{type NoRep[+T] = T}. In section \ref{stagedinterp}, \texttt{R} will be instantiated 
as a staging annotation. \todo{where talk about stage poly?}

@@

Address just record the variable name, more sensitivity in section ...

>>>>

As higher-order functions had been widely introduced in mainstream programming languages \todo{cite}, in this paper, 
we target a tiny higher-order functional language \TLang, which is based on direct-style lambda-calculus
with the support of numbers, arithmetics, recursions and conditionals.
In Section~\ref{cases_imp}, we will see adding more imperative features to the language.
Since we are mostly interested in analyzing the dynamic behavior of the program, the static semantics and
type system will be omitted. We also assume all the input programs are well-typed.
The abstract syntax is described below:

@@

Readers may notice an additional abstract type \texttt{R[+T]} is defined in the trait,
which means \texttt{R} represents a higher-kinded type and will used to specify the binding-time, 
i.e., staged or not. Since the LMS framework we are using allows us to specify binding-time purely
based on types, the unstaged higher-kinded type can be simply instantiated as an identity type constructor: 
\texttt{type NoRep[+T] = T}. In Section~\ref{stagedinterp}, \texttt{R} will be instantiated 
as a staging annotation. \todo{where talk about stage poly?}

@@

Address just record the variable name, more sensitivity in Section ...

### 2018-11-06 paper/50_cases.tex
section refs

The target language we presented in section \ref{bg_lang} is essentially a higher-order functional language.
One fundamental analysis task for functional programs is the control-flow analysis, i,e., determining
which functions will possibly be applied at each call-site. 
Though, in the previous section, we discussed abstraction compilation and staging on a monovariant 
control-flow analysis for programs written in continuation-passing style; 
in this section, based on the staged abstract interpreter we presented in section \ref{sai}, 
we further discuss staging control-flow analysis for direct style languages in depth, 
especially polyvariant analyses.

>>>>

The target language we presented in Section~\ref{bg_lang} is essentially a higher-order functional language.
One fundamental analysis task for functional programs is the control-flow analysis, i,e., determining
which functions will possibly be applied at each call-site. 
Though, in Section~\ref{?}, we discussed abstraction compilation and staging on a monovariant 
control-flow analysis for programs written in continuation-passing style; 
in this section, based on the staged abstract interpreter we presented in Section~\ref{sai}, 
we further discuss staging control-flow analysis for direct style languages in depth, 
especially polyvariant analyses.
